The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-06 paper/Analisis.tex
first version of the introduction

Performing that study is the main goal of this paper. We study for the
first time the impact of rotation on the morphology of the Lyman
$\alpha$ line. We focus on a simplified system, a spherical gas claud
with homogeneous density and solid body rotation. We base our work on two independent Monte
Carlo based radiative transfer codes CLARA \citep{CLARA} and XX
\citep{DijkstraKramer} .

This paper is paper is structured as follows...

@@

\section{Conclusions}
In this paper we have estimated the effects of gas bulk rotation on
the emission  of the Lyman $\alpha$ line. We based the study on the
study of a simplified configuration of an homogeneous sphere rotating
as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Ly$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line.

>>>>

Performing that study is the main goal of this paper. We investigate for the
first time the impact of rotation on the morphology of the Lyman
$\alpha$ line. We focus on a simplified system, a spherical gas cloud
with homogeneous density and solid body rotation. We focus our study
on the line morphology, anisotropic integrated emission and the escape
fraction in the presence of dust. We base our work on two independent
Monte Carlo based radiative transfer codes CLARA \citep{CLARA} and XX
\citep{DijkstraKramer} .

This paper is paper is structured as follows. In \S
\ref{sec:implementation} we present the implementation of bulk
rotation into the Monte Carlo codes, paying special attention to coordinate
definitions. There we also list the different physical parementers in
the simulated grid of models. In the next section we present the
results of the simulations, with special detail to quantities in the
line that show a clear evolution as a function of the cloud's
rotational velocity. In \S \ref{sec:dicussion} we discuss the
implications of our results in the interpretation of LAEs
observations and further refinements that can be implemented in the
theoretical modelling of the \ly line. In the last section we preset
our conclusiones.

@@

\section{Conclusions}
\label{sec:conclusions}
In this paper we have estimated the effects of gas bulk rotation on
the emission  of the Lyman $\alpha$ line. We based the study on the
study of a simplified configuration of an homogeneous sphere rotating
as a solid body. We explored  a range of models by varying the
rotation speed, hydrogen optical depth, dust optical depth and initial
distribution of Ly$\alpha$ photons with respect to the gas
density. This was implemented in CLARA, a Monte-Carlo
radiative transfer code already used to study the Lyman $\alpha$
line.
